Do motif roles provide unique information about species risk of extinction?\\ \medskip Supplementary Information

### 2021-09-29 manuscript/supplement_motifs.tex
methods synced

        S, C for random effects. $\Sigma$ and $\zeta$ for fixed effects.

@@

        \subsubsection{How does persistence vary with degree and trophic level?}

            A species’ motif participation is likely related to its in-degree and trophic level since all three properties are measures of network position. To provide context for the results above, we therefore fit two linear mixed-effects regressions relating persistence to degree or trophic level, $\pi_{disturbed}$, and their interaction. As above, we centered and scaled the predictors. We also included a random effect of the interaction between network size and connectance in order to account for the differences in persistence between different networks.

>>>>

@@

            \begin{equation}
                \Psi_{ik} \approx \Sigma_{i} + \zeta_{i} + \pi_{disturbed_k} + \Sigma_{i}:\zeta_{i} + \Sigma_{i}\pi_{disturbed_k} + \zeta_{i}\pi_{disturbed_k} + \Sigma_{i}\zeta_{i}\pi_{disturbed_k},
                \label{SCeq}
            \end{equation}
            where all symbols are as in equation~\ref{propreq} and~\ref{partic_SC}.

        \subsubsection{How does persistence vary with in-degree and trophic level?}

            Likewise, in-degree and trophic level are known to influence persistence in many cases.
            These effects, in combination with differences in mean persistence across networks with different global properties, should also be taken into account when considering relationships between motif participation and persistence.
            To establish this necessary context, we therefore fit two linear mixed-effects regressions:

            \begin{equation}
                    \Psi_{ik} \approx \delta_{i} + \pi_{disturbed_k} + \delta_{i}\pi_{disturbed_k} +
                    S_{i}C_{i} ,
                    \label{degeq}
                \end{equation}

            \begin{equation}
                    \Psi_{ik} \approx \tau_{i} + \pi_{disturbed_k} + \tau_{i}\pi_{disturbed_k} +
                    S_{i}C_{i} ,
                    \label{TLeq}
                \end{equation}

            where $\delta_{i}$ and $\tau_i$ are the in-degree and trophic level of species $i$, respectively, and all other terms are as in equation~\ref{propreq}.
            We centered and scaled the predictors before fitting the models.
